---
title: "DRI"
author: "Andrea Stocco"
date: "11/16/2016"
output:
  html_document:
    code_folding: hide
    theme: yeti
    toc: yes
    toc_depth: 3
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# DRI Experiment

```{r results="hide", warning=FALSE}
library(Rmisc)
library(matlab)
library(broom)
library(knitr)
library(dplyr)
library(pander)
source("functions.R")
```

First, we load the data

```{r}
data <- read.table("andrea_data.csv", header=T, sep=",")
```

Then, we need to convert the original binary data format into meaningful, named, factors:

```{r}
data$Instructed[data$Instructed == 0] <- "Inferred"
data$Instructed[data$Instructed == 1] <- "Instructed"

data$Rule[data$Rule == 0] <- "Symbolic"
data$Rule[data$Rule == 1] <- "Concrete"

data$Stimulation[data$Stimulation == 0] <- "Early"
data$Stimulation[data$Stimulation == 1] <- "Late"
data$Stimulation[data$Stimulation == 2] <- "NoStimulation"

data$Site[data$Site == 0] <- "PMd"
data$Site[data$Site == 1] <- "Vertex"

data$Subject <- as.factor(data$Subject)

data <- subset(data, data$Site != "NaN")
```

We can then perform a 2x2x3x2 ANOVA, with _Instructed_, _Rule_, _Stimulation_, and _Site_ as the factors, and _Subject_ as the random factor. 

```{r results="hide"}
acc <- aggregate(data[c("Accuracy")], list(Instructed=data$Instructed, Rule=data$Rule, 
                                           Stimulation=data$Stimulation, Site=data$Site,
                                           Subject=data$Subject),
                 mean)
  

model <- aov(acc$Accuracy ~ (Instructed * Rule * Stimulation * Site) 
            + Error(Subject/(Instructed * Rule * Stimulation * Site)), 
            acc)
```
```{r}
panderOptions("table.style", "rmarkdown")
panderOptions('digits', 3)
pander(model)
```
The we analyze the response times for correct trials only.

```{r}
correct <- subset(data, data$Accuracy == 1 & !is.na(data$ResponseTime))

d <- aggregate(correct[c("EncodingTime", "ResponseTime")], list(Instructed=correct$Instructed, 
                                                                Rule=correct$Rule, 
                                                                Stimulation=correct$Stimulation, 
                                                                Site=correct$Site,
                                                                Subject=correct$Subject),
                 mean)

model <- aov(EncodingTime ~ (Instructed * Rule * Stimulation * Site) 
             + Error(Subject/(Instructed * Rule * Stimulation * Site)), 
             d)

panderOptions("table.style", "rmarkdown")
panderOptions('digits', 3)
pander(model)
```
And one for the Response Time:

```{r}
model <- aov(EncodingTime ~ (Instructed * Rule * Stimulation * Site) 
             + Error(Subject/(Instructed * Rule * Stimulation * Site)), 
             d)

panderOptions("table.style", "rmarkdown")
panderOptions('digits', 3)
pander(model)
```

Now a close look at the stimulation data, omitting the "No-Stimulation" trials.

```{r}
ds <- subset(d, d$Stimulation != "NoStimulation")

model <- aov(ResponseTime ~ (Instructed * Stimulation * Rule * Site) 
            + Error(Subject/(Instructed * Stimulation * Rule * Site)), 
            ds)
panderOptions("table.style", "rmarkdown")
panderOptions('digits', 3)
pander(model)

```

Here is the corresponding graph for the critical effect

```{r}
k1 <- subset(ds, ds$Stimulation == "Late" & ds$Instructed == "Inferred")
ms <- tapply(k1$ResponseTime, list(k1$Site, k1$Rule), mean)
ses <- tapply(k1$ResponseTime, list(k1$Site, k1$Rule), se)
xs <- barplot(ms, beside = T, legend=T, 
        ylim=c(0,2), main="Inferred Rules, Late Stimulation", border="white", col=c("grey65", "grey45"))
arrows(x0=xs, x1=xs, y0=ms, y1 = ms + ses, angle=90)
arrows(x0=xs, x1=xs, y0=ms, y1 = ms - ses, angle=90)

# Adds some numbers
text(x = xs, y = ms + ses + 0.05, labels = round(ms, 3))
```